Higher-Order unification for free!

### 2024-04-11 paper/main.tex
add a citation to teyjus

% from https://www.cs.mcgill.ca/~bpientka/papers/unif_miller60.pdf
Working with terms in \llambda is sometime too restrictive \cite{Abel2018ExtensionsTM}. 
There exists systems
such as $\lambda$Prolog~\cite{lamProlog} which 
delay the resolution of \notllambda unification problems if the substitution
is not able to put them in \llambda. For example in 
\noteD{Teijus}
%
% make test ONLY=7005 TEX=tex
\printAlll
  {{{(X\appsep a),a},
    {X,\lambda x.Y}}}
  {{}}
  {{}}
  {{}}

>>>>

% from https://www.cs.mcgill.ca/~bpientka/papers/unif_miller60.pdf
Working with terms in \llambda is sometime too restrictive \cite{Abel2018ExtensionsTM}. 
There exists systems
such as Teyjus\cite{Nadathur2001} and $\lambda$Prolog~\cite{lamProlog} which 
delay the resolution of \notllambda unification problems if the substitution
is not able to put them in \llambda.
%
% make test ONLY=7005 TEX=tex
\printAlll
  {{{(X\appsep a),a},
    {X,\lambda x.Y}}}
  {{}}
  {{}}
  {{}}
